\begin{bio}

\textbf{Monojit Choudhury} is a Researcher at Microsoft Research India. His research interests cut across the areas of Linguistics, Cognition and Computation. Currently, he is working on script and code-mixing, especially in social media and web search. They have introduced the notion of Mixed-Script Information Retrieval, where the query and the documents can be in different, and possibly, more than one scripts but in the same language; the task is to retrieve the relevant documents across scripts. He is also interested in developing core NLP techniques for identifying and processing code-mixed text, and studying the extent, distribution and socio-linguistic factors influencing code-mixing.


\textbf{Kalika Bali} is a Researcher at Microsoft Research India. Her research interests lie broadly in the area of Speech and Language Technology especially in the use of linguistic models for building technology that offers a more natural Human-Computer as well as Computer-Mediated interactions. She is currently working on Project M\'elange where they try to understand, process and generate Code-mixed language data for both text and speech. She is also very passionate about NLP and Speech technology for Indian Languages. She believes that local language
technology especially with speech interfaces, can help millions of people gain entry into a world that is till now almost inaccessible to them. She has served, and continue to serve, on several government and other committees that work on Indian Language Technologies as well as Linguistic Resources and Standards for NLP/Speech.


\end{bio}

\begin{tutorial}
  {Processing and Understanding Mixed Language Data}
  {tutorial-final-002}
  {\daydateyear, \tutorialmorningtime}
  {\TutLocB}

Multilingual communities exhibit code-mixing, that is, mixing of two or more socially stable languages in a single conversation, sometimes even in a single utterance. This phenomenon has been widely studied by linguists and interaction scientists in the spoken language of such communities. However, with the prevalence of social media and other informal interactive platforms, code-switching is now also ubiquitously observed in user-generated text. As multilingual communities are more the norm from a global perspective, it becomes essential that code-switched text and speech are adequately handled by language technologies and NUIs.

Code-mixing is extremely prevalent in all multilingual societies. Current studies have shown that as much as 20\% of user generated content from some geographies, like South Asia, parts of Europe, and Singapore, are code-mixed. Thus, it is very important to handle code-mixed content as a part of NLP systems and applications for these geographies.

In the past 5 years, there has been an active interest in computational models for code-mixing with a substantive research outcome in terms of publications, datasets and systems. However, it is not easy to find a single point of access for a complete and coherent overview of the research. This tutorial is expecting to fill this gap and provide new researchers in the area with a foundation in both linguistic and computational aspects of code-mixing. We hope that this then becomes a starting point for those who wish to pursue research, design, development and deployment of code-mixed systems in multilingual societies.

\end{tutorial}
