\section{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}

\setlength{\parskip}{1ex}

Welcome to EMNLP-IJCNLP 2019 in Hong Kong! I hope that this will be a successful conference in the 25-year tradition of EMNLP and IJCNLP, as well as an enjoyable and enriching experience for all. Continuing recent trends, this year has seen overwhelming interest from researchers from all over the world. We received a total of 2,895 submissions (1,822 long and 1,073 short), which is a 36\% increase over EMNLP 2018 (2,117 submissions).

The three Program Co-Chairs, Jing Jiang, Vincent Ng, and Xiaojun Wan, oversaw the entire submission process, a truly herculean feat. I am deeply grateful for your support. Managing such a large number of submissions would not have been possible without the hard work of a whopping 152 Area Chairs headed by 18 Senior Area Chairs as well, each responsible for overseeing a broad area. Under them, the combined effort of over 1700 reviewers, each carefully examining submissions through the lens of their expertise, resulted in 466 long and 217 short papers to be presented at the main conference. Your efforts have been indispensable for making this conference happen. 
 
I would like to express special thanks to Priscilla Rasmussen, the ACL Business Manager, who has been indispensable through many years of not only EMNLP but many other key NLP conferences. All of this would not have been possible without you. My deepest gratitude to David Yarowsky, Jian Su, and Noah Smith, and many others from the SIGDAT and AFNLP boards for their invaluable guidance in navigating difficult issues surrounding the daunting task I was faced with. 
 
The hard work of our hosts, the Local Organizing Committee chair Kam-Fai Wong and members Samuel Tam, Emmanuele Chersoni, Churen Huang, Wenjie Li, Derek F. Wong, and Ruifeng Xu, have especially been vital in bringing together EMNLP-IJCNLP 2019.

As many as 17 workshops and a co-located conference, CoNLL, have been coordinated by the Workshop Chairs Vera Demberg and Naoaki Okazaki. EMNLP-IJNLP 2019 will also be hosting a full-day tutorial and six half-day tutorials brought together by the Tutorial Chairs Timothy Baldwin and Marine Carpuat. The combined efforts of the Demonstration Chairs Sebastian Padó and Ruihong Huang have culminated in a total of 44 accepted demo papers out of 110 submissions in addition to the overwhelming main conference papers. I am deeply grateful for your endless labor that brought to fruition an exciting program I am truly proud to be a part of. 
We sought to make EMNLP 2019 a venue that is as welcoming and inclusive as possible to all. In this effort, we worked on continuing and expanding the diversity and inclusion (D&I) efforts initiated in recent NLP conferences and also the Widening NLP workshop.  The D&I committee, co-chaired by Vivek Srikumar and Chi-Kiu (Jackie) Lo, coordinated with the Childcare Policy and Grant Coordinators Olivia Kwong and Sujian Li to help remove any obstacles to participating in a key event in the NLP community. Student Volunteer Coordinator and Student Scholarship Chair Wenjie Li and Marzieh Saeidi coordinated providing scholarships to students and non-students wanting to join us, who otherwise might not have had the means to. The D&I committee focused on several initiatives involving mentoring, both for first-time conference attendees and otherwise, providing accommodations and improving accessibility for participants if necessary, and generally making the conference experience a broadly comfortable one. We hope that these efforts at making EMNLP inclusive and welcoming will help enrich the conference.

A warm thank you to Micha Elsner, the General Publication Chair, Publication Chairs Fei Liu and Pontus Stenetorp, and also to Serena Villata, the Conference Handbook Chair, Kai-Wei Chang, the Conference Handbook Advisor, Natalie Schluter, the Conference Handbook Proofreader, for their strong sense of duty resulting in excellent supporting materials, arguably the most important contribution to many! I must also thank Publicity Chairs Wei Xu and Sebastian Ruder, and Website and Conference App Chairs Kevin Duh and Henning Wachsmuth for your excellent promotion. We owe our success to reaching all those that could be interested, which cultivated a strong interest within the NLP community.

Last but not least, I would like to express my deepest gratitude to our sponsors, whose generous support has been invaluable in building up EMNLP and IJCNLP to what it is now. A special thank you to Google, Facebook, MEHK, Apple, ASAPP, and Salesforce, our Diamond sponsors. Many thanks to our Platinum sponsors Huawei, Baidu, GTCOM, DeepMind, and Amazon. We are also profoundly grateful to our Gold level sponsors PolyAI, Naver, ByteDance, Megagon Labs, Zhuiyi Technology, and Verisk Analytics, Silver level sponsors Duolingo, SAP, Babelscape, eBay, and Cisco, and finally, our Bronze level sponsors the USC Viterbi School of Engineering and Shannon.AI as well. 
Thank you for your monumental support towards hosting another (hopefully!) successful year of EMNLP-IJCNLP. 
 
Finally, I would like to once again welcome you to EMNLP-IJCNLP 2019! We hope that this will be an exciting and memorable experience for you, especially if you are joining us for the first time. The NLP community is as thriving as ever, and I am honored to have had a part in hosting one of the leading conferences in the area of Natural Language Processing.


\vspace{3em}
\noindent
EMNLP-IJCNLP 2019 General Chair\\


\noindent{\it Kentaro Inui}, Tohoku University, Japan\\


\index{Inui, Kentaro}


